Deep mutational scanning of hemagglutinin helps predict evolutionary fates of human H3N2 influenza variants

### 2018-04-09 paper/manuscript.tex
Updated date interval and number of strains sampled for phylogeny.

\subsection*{Inference of human H3N2 phylogenetic tree and calculation of maximum mutation frequencies}
To generate the tree shown in Figure~\ref{suppfig:tree}, we applied Nextstrain's augur pipeline~\cite{Hadfield224048} (\url{https://github.com/nextstrain/augur}; commit \texttt{006896d}) to publicly available H3N2 HA sequences from GISAID \cite{shu2017gisaid} (see Dataset~\ref{suppdata:gisaid}), sampling six viruses per month over the time interval of January 1, 1968 to April 1, 2017.
We aligned the resulting 2,139 HA sequences with MAFFT v7.310~\cite{katoh2013mafft} and constructed a maximum likelihood phylogeny from this alignment with RAxML 8.2.10~\cite{stamatakis2006raxml}.
Ancestral state reconstruction and branch length timing were performed with TreeTime~\cite{Sagulenko2018}.
We pruned seven strains with premature stop codons in their amino acid translations that represented likely sequencing errors, producing a final tree with 2,132 strains.
The phylogenetic tree is available as a JSON file on GitHub at \url{https://github.com/jbloomlab/Perth2009-DMS-Manuscript/blob/master/analysis_code/data/flu_h3n2_ha_1968_2018_6v_tree.json.gz}.
The tree was visualized using BALTIC (\url{https://github.com/blab/baltic}).

>>>>

\subsection*{Inference of human H3N2 phylogenetic tree and calculation of maximum mutation frequencies}
To generate the tree shown in Figure~\ref{suppfig:tree}, we applied Nextstrain's augur pipeline~\cite{Hadfield224048} (\url{https://github.com/nextstrain/augur}; commit \texttt{006896d}) to publicly available H3N2 HA sequences from GISAID \cite{shu2017gisaid} (see Dataset~\ref{suppdata:gisaid}), sampling six viruses per month over the time interval of January 1, 1968 to February 1, 2018.
We aligned the resulting 2,189 HA sequences with MAFFT v7.310~\cite{katoh2013mafft} and constructed a maximum likelihood phylogeny from this alignment with RAxML 8.2.10~\cite{stamatakis2006raxml}.
Ancestral state reconstruction and branch length timing were performed with TreeTime~\cite{Sagulenko2018}.
The phylogenetic tree is available as a JSON file on GitHub at \url{https://github.com/jbloomlab/Perth2009-DMS-Manuscript/blob/master/analysis_code/data/flu_h3n2_ha_1968_2018_6v_tree.json.gz}.
The tree was visualized using BALTIC (\url{https://github.com/blab/baltic}).
